---
title: "Financial Time Series Plotting"
author: "Olumide Michael Oyalola"
date: "September 21, 2018"
output: 
  html_document: 
    fig_caption: yes
    toc: yes
    number_sections: false
    toc_depth: 4
    fig.retina: 4
    fig.caption: true
    fig.width: 12
    fig.height: 7
    code_folding: show
    df_print: paged
    toc_float: 
      collapsed:  false
      smooth_scroll: false
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

### Loading the required libraries

```{r packages}

library(tidyverse)
library(zoo)
library(xts)
library(highcharter)
library(lubridate)
library(dygraphs)
```


### Reading the required datasets

```{r readdata}

eur_gbp_hist_df <- read_csv("EUR_GBP Historical Data.csv", col_names = TRUE, trim_ws = TRUE) %>%
  mutate(Date = as.Date(as.yearmon(Date, format = "%b %y")))

eur_usd_hist_df <- read_csv("EUR_USD Historical Data.csv", col_names = TRUE, trim_ws = TRUE) %>%
  mutate(Date = as.Date(as.yearmon(Date, format = "%b %y")))

gbp_usd_hist_df <- read_csv("GBP_USD Historical Data.csv", col_names = TRUE, trim_ws = TRUE) %>%
  mutate(Date = as.Date(as.yearmon(Date, format = "%b %y")))

germany_5yr_bond_yield_df <- read_csv("Germany 5-Year Bond Yield Historical Data.csv", col_names = TRUE, trim_ws = TRUE) %>%
  mutate(Date = as.Date(as.yearmon(Date, format = "%b %y")))

uk_5yr_bond_yield_df <- read_csv("United Kingdom 5-Year Bond Yield Historical Data.csv", col_names = TRUE, trim_ws = TRUE) %>%
  mutate(Date = as.Date(as.yearmon(Date, format = "%b %y")))

usa_5yr_bond_yield_df <- read_csv("United States 5-Year Bond Yield Historical Data.csv", col_names = TRUE, trim_ws = TRUE) %>%
  mutate(Date = as.Date(as.yearmon(Date, format = "%b %y")))

```

### Data Prepping

#### Computing the monthly prices of spread between countries

```{r spread}

eur_gbp_spread_df <- germany_5yr_bond_yield_df %>%
  inner_join(uk_5yr_bond_yield_df, by = "Date") %>%
  mutate(Ratio = Price.x/Price.y) %>%
  select(Date, Ratio)

eur_usd_spread_df <- germany_5yr_bond_yield_df %>%
  inner_join(usa_5yr_bond_yield_df, by = "Date") %>%
  mutate(Ratio = Price.x/Price.y) %>%
  select(Date, Ratio)

gbp_usd_spread_df <- uk_5yr_bond_yield_df %>%
  inner_join(usa_5yr_bond_yield_df, by = "Date") %>%
  mutate(Ratio = Price.x/Price.y) %>%
  select(Date, Ratio)

```


#### Merging the Spread between countries and the corresponding nominal historical exchange rate

```{r mergeSpreadandExchange}

eur_gbp_compare <- eur_gbp_hist_df %>% select(Date, Price) %>%
  inner_join(eur_gbp_spread_df, by = "Date") %>%
  select(-Date) %>%
  ts(start = c(1987, 7), frequency = 12)

eur_usd_compare <- eur_usd_hist_df %>% select(Date, Price) %>%
  inner_join(eur_usd_spread_df, by = "Date") %>%
  select(-Date) %>%
  ts(start = c(1987, 7), frequency = 12)

gbp_usd_compare <- gbp_usd_hist_df %>% select(Date, Price) %>%
  inner_join(gbp_usd_spread_df, by = "Date") %>%
  select(-Date) %>%
  ts(start = c(1987, 7), frequency = 12)

```

### Visualizations

### EUR_GBP spread and Nominal Exchange Rate Series

```{r eur_gbp_compare, fig.height=6, fig.width=10}

dygraph(eur_gbp_compare) %>%
  dySeries("Price", label = "Ex Rate") %>%
  dySeries("Ratio", label = "Spread") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 30)

```


### EUR_USD spread and Nominal Exchange Rate Series

```{r eur_usd_compare, fig.height=6, fig.width=10}

dygraph(eur_usd_compare) %>%
  dySeries("Price", label = "Ex Rate") %>%
  dySeries("Ratio", label = "Spread") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 30)

```


### GBP_USD spread and Nominal Exchange Rate Series

```{r gbp_usd_compare, fig.height=6, fig.width=10}

dygraph(gbp_usd_compare) %>%
  dySeries("Price", label = "Ex Rate") %>%
  dySeries("Ratio", label = "Spread") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 30)

```
